---
title: Customer Behavior Analysis and Predictive Modelling of Telco Campaign Offer
  Taker
author: "Yin Khar Shin, Sam Kar Hong, Rose Tiong, Lee Wei Qin, Chua Xing Zhao"
date: "2023-04-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this report, we will explore the mtcars dataset to gain insights into the relationship between car attributes and fuel efficiency.

## Load Libraries

We will start by loading the necessary libraries for our analysis:

```{r load-libraries, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(caret)
library(ggplot2)
library(tidymodels)
```

## Load Dataset
Next, we will load the `mtcars` dataset:

```{r data}
data(mtcars)
head(mtcars)
```
## EDA

To gain a better understanding of our data, we will perform some exploratory data analysis (EDA). We will start by looking at the summary statistics of our data:

```{r cars}
summary(cars)
```

## Visualizations
Next, we will create some visualizations to explore the relationships between our variables:

```{r visuals, echo=FALSE}
# Scatterplot matrix of mtcars dataset
ggplot(mtcars, aes(x = mpg, y = wt)) + geom_point() +
  labs(title = "Scatterplot Matrix of mtcars dataset")
```

Based on the scatterplot matrix, we can see that there is a negative relationship between mpg (miles per gallon) and wt (weight). This suggests that lighter cars tend to have higher miles per gallon.

## Modeling
To investigate the relationship between mpg and wt in more detail, let's fit a linear regression model:

```{r mod, echo=TRUE}
# Fit a linear regression model
lm_fit <- lm(mpg ~ wt, data = mtcars)

# Print the summary of the model
summary(lm_fit)
```

The summary of the model shows that there is a statistically significant negative relationship between mpg and wt. Specifically, for every unit increase in weight, mpg decreases by 5.344.

We can also use the caret package to perform cross-validation and assess the accuracy of the model:

```{r result, echo=TRUE}
# Use 10-fold cross-validation to assess the accuracy of the model
lm_cv <- train(mpg ~ wt, data = mtcars, method = "lm", trControl = trainControl(method = "cv", number = 10))

# Print the accuracy of the model
lm_cv$results$RMSE
```
The root mean squared error (RMSE) of the model is 2.967, which suggests that the model has decent accuracy.

## Conclusion

In this report, we explored the mtcars dataset using R and investigated the relationship between mpg and wt. We found that there is a statistically significant negative relationship between the two variables, with lighter cars tending to have higher miles per gallon. We also fit a linear regression model and used cross-validation to assess its accuracy. Overall, our findings suggest that weight is an important predictor of miles per gallon for the automobiles in the mtcars dataset.